Contracts for unions and intersections are hard for Nickel

### 2021-05-27 paper.tex
Small fixes and trailing spaces

Beyond CSE, optimizations such as loop-invariant code motion or
let-floating~\ref{} apply the same principle of extracting an invariant
expression to avoid recomputation respectively across loop iterations and
function calls. For example, take the code of
Figure~\ref{fig:optimizations-let-floating-ex}.

@@

The partial application \lstinline+g y+ is recomputed each time \lstinline+f+ is
called. This may be costly, in particular in the presence of contracts: if
\lstinline+y+ is a list for example, and \lstinline+g+ applies a list contract
on it, the cost could be linear in the size of \lstinline+y+. A sensible thing
to do is to factor \lstinline+g y+ out of \lstinline+f+ as in
Figure~\ref{fig:optimizations-let-floating-ex}, which is something a
let-floating transformation could indeed do (given \lstinline+g+ is pure, as
explained below).

>>>>

Beyond CSE, optimizations such as loop-invariant code motion or
let-floating~\ref{} apply the same principle of extracting out an invariant
expression to avoid its recomputation respectively across loop iterations and
function calls.

@@

For example, take the code of Figure~\ref{fig:optimizations-let-floating-ex}.
The partial application \lstinline+g y+ is recomputed each time \lstinline+f+ is
called. This may be costly, in particular in the presence of contracts: if
\lstinline+y+ is a list for example, and \lstinline+g+ applies a list contract
on it, the cost could be linear in the size of \lstinline+y+. A sensible thing
to do is to factor \lstinline+g y+ out of \lstinline+f+ as in
Figure~\ref{fig:optimizations-let-floating-ex}, which is something a
let-floating transformation could indeed do (given \lstinline+g+ is pure, as
explained below).
